---
output: 
  latex_document:
    latex_engine: xelatex
    template: "./cv-simple.tex"
    md_extensions: "-autolink_bare_uris"

name: "Jacob A. Long"

title: "Ph.D Candidate"
affiliation: "School of Communication \\hspace{.05in} \\textbullet \\hspace{.05in} Ohio State University"
contact:
  - text: "long.1377@osu.edu"
    link: "mailto:long.1377@osu.edu"
    icon: "EnvelopeO"
    mono: false
  - text: "jacob-long.com"
    link: "https://jacob-long.com"
    icon: "Globe"
    mono: true
  - text: "jacob-long"
    link: "https://github.com/jacob-long"
    icon: "Github"
    mono: true
  - text: "0000-0002-1582-6214"
    link: "https://orcid.org/0000-0002-1582-6214"
    acad: "Orcid"
    mono: true
# twitter: jacobandrewlong

bibs:
  - "pubbed.bib"
  - "conferences.bib"
  - "inprogress.bib"
  - "review.bib"

namehash: "7ee2eb84ac3fb6ae0cc177587fcaff6a"

raggedright: true

colorlinks: true
linkcolor: "blue"
urlcolor: "magenta"
---

```{r setup, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE, warn = FALSE, message = FALSE, comment = "")
```

# Education

## The Ohio State University, \normalfont Columbus, Ohio USA

* Ph.D Candidate, Communication (expected graduation: Spring 2020)

    * Committee: 

        \smallskip

        William P. "Chip" Eveland, Jr. (advisor) 
        \hspace{.05in} \textbullet \hspace{.05in} Michael D. Slater
        \hspace{.05in} \textbullet \hspace{.05in} Gerald M. Kosicki
        \hspace{.05in} \textbullet \hspace{.05in} Robert M. Bond

        \smallskip

    * Graduate Interdisciplinary Specialization in Survey Research

* M.A., Communication, 2019

## Rhodes College, \normalfont Memphis, Tennessee USA

* B.A. with Honors, Political Science, 2014

    * Minors in Film Studies and English
    * Honors Thesis: "Understanding *The Daily Show with Jon Stewart*:
        Effects in a New Media Environment"
    * Advisors: Amy E. Jasperson and Rashna Wadia Richards

# Publications

```{r results = 'asis'}
library(RefManageR)
print_refs <- function(file) {
  refs <- ReadBib(file, check = FALSE)
  cat(paste0("\\fullcitebib{", paste(names(sort(refs, sorting = "ydnt")), collapse = ", "), "}"))
}
print_refs("pubbed.bib")
```

# Under Review

```{r results = 'asis'}
print_refs("review.bib",  c("garrett"))
```


# Conference Presentations 

```{r results = 'asis'}
print_refs("conferences.bib")
```

\newpage

# Software

## R Packages

`jtools`: Analysis and presentation of social scientific data. 

```{r echo = FALSE}
library(rvest)
library(magrittr)
prof_url <- "https://scholar.google.com/citations?hl=en&user=fi-oVkIAAAAJ&view_op=list_works&citft=1&citft=2&email_for_op=jlongrc%40gmail.com&gmla=AJsN-F6U0W7Pb2H2sGdtSobMNTJR-HLu-OQ8kKCZeXg1EycF_GfWYLB54v7H5SlMcGBqKUjGlMnSkJlG3j0fM8wMhBJz2i4iM5kAVUf2PeoGyCMgeTkkLwA&gmla=AJsN-F7fklbe6gqvPjDweKtwwyvicMTZxtpVLPRUTNteYwXL1tMV7xHD81vwhCXcs_suOKGI83V7y8c_R5a_GxNBIkkarl0D6W7yKCwU2m9JqJ0Mzupk46M&sciund=729968478779288"
read_html(prof_url) %>%
  html_nodes("tr.gsc_a_tr") %>%
  .[stringr::str_detect(html_text(.), "jtools")] %>%
  html_children() %>%
  html_text() %>%
  .[2] -> jtools_gsch

library(jsonlite)
url <- paste0("https://cranlogs.r-pkg.org/downloads/total/2014-01-01:", Sys.Date(), "/jtools")
jtools_cranlogs <- fromJSON(url)[["downloads"]]
```

\small
\vspace{-.05in}

* \faicon{r-project} [CRAN](https://CRAN.R-project.org/package=jtools) 
\hspace{.03in} \textbullet \hspace{.05in} 
\faGithub \hspace{.02in} [jacob-long/jtools](https://github.com/jacob-long/jtools)
\hspace{.03in} \textbullet \hspace{.05in} 
\faGlobe \hspace{.02in} [jtools.jacob-long.com](https://jtools.jacob-long.com)

* Author: **Jacob A. Long**
    * `r jtools_gsch` scholarly citations per
    [Google Scholar](https://scholar.google.com/scholar?oi=bibs&hl=en&cites=9332474636617245381,8245268343852705630) as of `r format(Sys.Date(), "%m/%d/%Y")`
    * `r format(jtools_cranlogs, big.mark = ",", scientific = FALSE)` downloads from RStudio's
    [CRAN mirror](https://r-pkg.org/services#cranlogs) as of `r format(Sys.Date(), "%m/%d/%Y")`

```{r echo = FALSE}
library(jsonlite)
url <- paste0("https://cranlogs.r-pkg.org/downloads/total/2014-01-01:", Sys.Date(), "/interactions")
interactions_cranlogs <- fromJSON(url)[["downloads"]]
```

\normalsize 

`interactions`: Comprehensive, user-friendly toolkit for probing interactions.

\small 
\vspace{-.05in}

* \faicon{r-project} [CRAN](https://CRAN.R-project.org/package=interactions) 
\hspace{.03in} \textbullet \hspace{.05in} 
\faGithub \hspace{.02in} [jacob-long/interactions](https://github.com/jacob-long/interactions)
\hspace{.03in} \textbullet \hspace{.05in} 
\faGlobe \hspace{.02in} [interactions.jacob-long.com](https://interactions.jacob-long.com)
* Author: **Jacob A. Long**
    * `r format(interactions_cranlogs, big.mark = ",", scientific = FALSE)` downloads from RStudio's
    [CRAN mirror](https://r-pkg.org/services#cranlogs) as of `r format(Sys.Date(), "%m/%d/%Y")`

\normalsize

`panelr`: Regression models and utilities for repeated measures and panel data.

\small 
\vspace{-.05in}

* \faGithub \hspace{.02in} [github.com/jacob-long/panelr](https://github.com/jacob-long/panelr)
\hspace{.03in} \textbullet \hspace{.05in} 
\faGlobe \hspace{.02in} [panelr.jacob-long.com](https://panelr.jacob-long.com)
* Author: **Jacob A. Long**

\normalsize

`dpm`: Dynamic panel models fit with maximum likelihood. 
\small 
\vspace{-.05in}

* \faGithub \hspace{.02in} [github.com/jacob-long/dpm](https://github.com/jacob-long/dpm)
\hspace{.03in} \textbullet \hspace{.05in} 
\faGlobe \hspace{.02in} [dpm.jacob-long.com](https://dpm.jacob-long.com)

* Authors: **Jacob A. Long**, Richard A. Williams, Paul D. Allison

\normalsize

## Other

Song and Lyric Data Scraper [Ruby app]. Accompanies Long \& Eveland (2019). 

\vspace{-.05in}

* doi:[10.5281/zenodo.1203368](https://doi.org/10.5281/zenodo.1203368)

\small 
\vspace{-.07in}

* \faGithub \hspace{.02in} [github.com/jacob-long/song-and-lyric-data-scraper](https://github.com/jacob-long/song-and-lyric-data-scraper) 

\normalsize


# Research in Progress

```{r results = 'asis'}
print_refs("inprogress.bib")
```

# Teaching

## Ohio State University

* COMM 4820: Public Opinion and Communication
    * Summer 2016

* COMM 3597: Media and Terrorism
    * Autumn 2018

* COMM 3554: Social Implications of Communication Technology
    * Summer 2018 (taught online)

* COMM 2367: Persuasive Communication
    * Autumn 2015, Spring 2016 (2 sections), Autumn 2016 (2 sections), Spring 2017 (taught online)

# Honors and Awards

University Fellowship (Ohio State University), 2014-15.

Mike Cody Award for Excellence in Political Science (Rhodes College), 2014.

Sigma Tau Delta, International English Honor Society, 2014.

Pi Sigma Alpha, National Political Science Honor Society, 2013.

Cambridge Scholarship (Rhodes College), 2010-14.

Robert C. Byrd Honors Scholarship, 2010-11.

# Professional Experience

## Freelance, WMC-TV 5, \normalfont Memphis, TN
Followed experience as news intern. Participated in editorial meetings, assisted reporters, anchors,
and producers, and worked assignment desk on weekends. Wrote content for newscasts and web.

# Service

## Conference Reviewing

*International Communication Association:*

* Mass Communication Division (2018)
* Political Communication Division (2018, 2019)
* Computational Methods Interest Group (2019)

*National Communication Association:*

* Mass Communication Division (2017)
* Political Communication Division (2017)

