---
output: 
  pdf_document:
    latex_engine: xelatex
    citation_package: "biblatex"
    template: "./cv-simple.tex"
    md_extensions: "-autolink_bare_uris -auto_identifiers"

name: "Jacob A. Long"

title: "Assistant Professor"
affiliation: "School of Journalism and Mass Communications \\hspace{.05in} \\textbullet \\hspace{.05in} University of South Carolina"
contact:
  - text: "jacob.long@sc.edu"
    link: "mailto:jacob.long@sc.edu"
    icon: "Envelope"
    opts: "regular"
    mono: false
  - text: "jacob-long.com"
    link: "https://jacob-long.com"
    icon: "Globe"
    mono: true
  - text: "jacob-long"
    link: "https://github.com/jacob-long"
    icon: "Github"
    mono: true
  - text: "0000-0002-1582-6214"
    link: "https://orcid.org/0000-0002-1582-6214"
    acad: "Orcid"
    mono: true
# twitter: jacobandrewlong

bibs:
  - "pubbed.bib"
  - "conferences.bib"
  - "inprogress.bib"
  - "review.bib"
  - "press.bib"

namehash: "7ee2eb84ac3fb6ae0cc177587fcaff6a"

raggedright: true

colorlinks: true
linkcolor: "blue"
urlcolor: "magenta"
---

```{r setup, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, comment = "")
```

# Appointments

## University of South Carolina \normalfont Columbia, South Carolina, USA

### School of Journalism and Mass Communications 

\vspace{-.05in}

* Assistant Professor \hfill 2020--

    
# Education

## The Ohio State University \normalfont Columbus, Ohio, USA

* PhD, Communication \hfill 2020

    * Dissertation: 
    
        \smallskip
    
        ``Time Dynamics and Stability of Political Identity and Political Communication''

    * Committee: 

        \smallskip

        William P. "Chip" Eveland, Jr. (advisor) 
        \hspace{.05in} \textbullet \hspace{.05in} Michael D. Slater 
      
        Gerald M. Kosicki \hspace{.05in} \textbullet 
        \hspace{.05in} Christopher R. Browning (Sociology)
      
        \smallskip

    * Graduate Interdisciplinary Specialization in Survey Research

* MA, Communication \hfill 2019

## Rhodes College \normalfont Memphis, Tennessee, USA

* BA with Honors, Political Science \hfill 2014

    * Minors in Film Studies and English
    * Advisors: Amy E. Jasperson and Rashna Wadia Richards

# Publications

```{r results = 'asis'}
library(RefManageR)
library(jtools)
print_refs <- function(file, names = NULL) {
  refs <- ReadBib(file, check = FALSE)
  cat(paste0("\\fullcitebib{", paste(
      c(names(refs) %just% names, names(sort(refs, sorting = "ydnt")) %not% names), 
      collapse = ", "), "}"
    )
  )
}
print_refs("pubbed.bib")
```

# Software

## R Packages

### `jtools`: Analysis and presentation of social scientific data. 

```{r echo = FALSE}
library(rvest)
library(magrittr)
prof_url <- "https://scholar.google.com/citations?hl=en&user=fi-oVkIAAAAJ&view_op=list_works&citft=1&citft=2&email_for_op=jlongrc%40gmail.com&gmla=AJsN-F6U0W7Pb2H2sGdtSobMNTJR-HLu-OQ8kKCZeXg1EycF_GfWYLB54v7H5SlMcGBqKUjGlMnSkJlG3j0fM8wMhBJz2i4iM5kAVUf2PeoGyCMgeTkkLwA&gmla=AJsN-F7fklbe6gqvPjDweKtwwyvicMTZxtpVLPRUTNteYwXL1tMV7xHD81vwhCXcs_suOKGI83V7y8c_R5a_GxNBIkkarl0D6W7yKCwU2m9JqJ0Mzupk46M&sciund=729968478779288"
read_html(prof_url) %>%
  html_nodes("tr.gsc_a_tr") %>%
  .[stringr::str_detect(html_text(.), "jtools")] %>%
  html_children() %>%
  html_text() %>%
  .[2] %>%
  stringr::str_replace_all("\\*", "") -> jtools_gsch

read_html(prof_url) %>%
    html_nodes("tr.gsc_a_tr") %>%
    .[stringr::str_detect(html_text(.), "jtools")] %>%
    html_nodes("a") %>% 
    html_attr("href") %>%
    .[stringr::str_detect(., "scholar\\.google\\.com")] -> jtools_gsch_link

read_html(prof_url) %>%
  html_nodes("tr.gsc_a_tr") %>%
  .[stringr::str_detect(html_text(.), "interactions")] %>%
  html_children() %>%
  html_text() %>%
  .[2] %>%
  stringr::str_replace_all("\\*", "") -> ints_gsch

read_html(prof_url) %>%
    html_nodes("tr.gsc_a_tr") %>%
    .[stringr::str_detect(html_text(.), "interactions")] %>%
    html_nodes("a") %>% 
    html_attr("href") %>%
    .[stringr::str_detect(., "scholar\\.google\\.com")] -> ints_gsch_link

jtools_gsch <- as.numeric(jtools_gsch) - as.numeric(ints_gsch)

library(jsonlite)
url <- paste0("https://cranlogs.r-pkg.org/downloads/total/2014-01-01:", Sys.Date(), "/interactions")
interactions_cranlogs <- fromJSON(url)[["downloads"]]

library(jsonlite)
url <- paste0("https://cranlogs.r-pkg.org/downloads/total/2014-01-01:", Sys.Date(), "/jtools")
jtools_cranlogs <- fromJSON(url)[["downloads"]]
```

\small
\vspace{-.05in}

* \faRProject \ [CRAN](https://CRAN.R-project.org/package=jtools) 
\hspace{.03in} \textbullet \hspace{.05in} 
\faGithub \hspace{.02in} [jacob-long/jtools](https://github.com/jacob-long/jtools)
\hspace{.03in} \textbullet \hspace{.05in} 
\faGlobe \hspace{.02in} [jtools.jacob-long.com](https://jtools.jacob-long.com)

    * `r jtools_gsch` scholarly citations per
    [Google Scholar](`r jtools_gsch_link`) as of `r format(Sys.Date(), "%m/%d/%Y")`
    * `r format(jtools_cranlogs, big.mark = ",", scientific = FALSE)` downloads from RStudio's
    [CRAN mirror](https://r-pkg.org/services#cranlogs) as of `r format(Sys.Date(), "%m/%d/%Y")`

```{r echo = FALSE}
## Until Scholar distinguishes these correctly, need to process this 
## earlier in the document
# read_html(prof_url) %>%
#   html_nodes("tr.gsc_a_tr") %>%
#   .[stringr::str_detect(html_text(.), "interactions")] %>%
#   html_children() %>%
#   html_text() %>%
#   .[2] %>%
#   stringr::str_replace_all("\\*", "") -> ints_gsch
# 
# read_html(prof_url) %>%
#     html_nodes("tr.gsc_a_tr") %>%
#     .[stringr::str_detect(html_text(.), "interactions")] %>%
#     html_nodes("a") %>% 
#     html_attr("href") %>%
#     .[stringr::str_detect(., "scholar\\.google\\.com")] -> ints_gsch_link
# 
# library(jsonlite)
# url <- paste0("https://cranlogs.r-pkg.org/downloads/total/2014-01-01:", Sys.Date(), "/interactions")
# interactions_cranlogs <- fromJSON(url)[["downloads"]]
```

\newpage

\normalsize 

### `interactions`: Comprehensive, user-friendly toolkit for probing interactions.

\small 
\vspace{-.05in}

* \faRProject \ [CRAN](https://CRAN.R-project.org/package=interactions) 
\hspace{.03in} \textbullet \hspace{.05in} 
\faGithub \hspace{.02in} [jacob-long/interactions](https://github.com/jacob-long/interactions)
\hspace{.03in} \textbullet \hspace{.05in} 
\faGlobe \hspace{.02in} [interactions.jacob-long.com](https://interactions.jacob-long.com)

    * `r ints_gsch` scholarly citations per
    [Google Scholar](`r ints_gsch_link`) as of `r format(Sys.Date(), "%m/%d/%Y")`
    * Reviewed favorably by 
    [Lin (2020)](https://doi.org/10.1080/10705511.2020.1732826) in the journal
    *Structural Equation Modeling*.
    * `r format(interactions_cranlogs, big.mark = ",", scientific = FALSE)` downloads from RStudio's
    [CRAN mirror](https://r-pkg.org/services#cranlogs) as of `r format(Sys.Date(), "%m/%d/%Y")`
    * Highlighted as a [top new package](https://rviews.rstudio.com/2019/03/26/february-2019-top-40-new-cran-packages/)
     in February 2019

\normalsize

### `panelr`: Regression models and utilities for repeated measures and panel data.

```{r echo = FALSE}
library(jsonlite)
url <- paste0("https://cranlogs.r-pkg.org/downloads/total/2014-01-01:", Sys.Date(), "/panelr")
panelr_cranlogs <- fromJSON(url)[["downloads"]]
```

\small 
\vspace{-.05in}

* \faRProject \ [CRAN](https://CRAN.R-project.org/package=panelr) 
\hspace{.03in} \textbullet \hspace{.05in} 
\faGithub \hspace{.02in} [jacob-long/panelr](https://github.com/jacob-long/panelr)
\hspace{.03in} \textbullet \hspace{.05in} 
\faGlobe \hspace{.02in} [panelr.jacob-long.com](https://panelr.jacob-long.com)

    * `r format(panelr_cranlogs, big.mark = ",", scientific = FALSE)` downloads from RStudio's
    [CRAN mirror](https://r-pkg.org/services#cranlogs) as of `r format(Sys.Date(), "%m/%d/%Y")`


\normalsize

### `dpm`: Dynamic panel models fit with maximum likelihood. 

\small 
\vspace{-.05in}

* \faGithub \hspace{.02in} [github.com/jacob-long/dpm](https://github.com/jacob-long/dpm)
\hspace{.03in} \textbullet \hspace{.05in} 
\faGlobe \hspace{.02in} [dpm.jacob-long.com](https://dpm.jacob-long.com)

* Authors: **Jacob A. Long**, Richard A. Williams, Paul D. Allison

\normalsize

I am also a contributor to the [`easystats`](https://easystats.github.io/blog/)
project, which is developing a suite of R packages to facilitate simple and
accessible statistical analysis.

## Other

Song and Lyric Data Scraper [Ruby app]. Accompanies Long \& Eveland (2019). 

\vspace{-.05in}

* doi:[10.5281/zenodo.1203368](https://doi.org/10.5281/zenodo.1203368)

\small 
\vspace{-.07in}

* \faGithub \hspace{.02in} [github.com/jacob-long/song-and-lyric-data-scraper](https://github.com/jacob-long/song-and-lyric-data-scraper) 

\normalsize

# Media

```{r results = 'asis'}
library(RefManageR)
library(jtools)
print_refs("press.bib")
```

# Conference Presentations 

```{r results = 'asis'}
BibOptions(check.entries = FALSE)
source("biblatex_hacks.R")
confs <- ReadBib("conferences.bib")
for (entry in names(confs)) {
  if (is.null(confs[[entry]]$note)) {
    confs[[entry]]$note <- paste(
    ifelse(is.null(confs[[entry]]$type), no = confs[[entry]]$type, yes = "Paper"),
    "presented at the", confs[[entry]]$eventtitle
    )
    confs[[entry]]$type <- NULL
  }
  
  for (i in 1:length(confs[[entry]]$author)) {
    if ("Jr." %in% confs[[entry]]$author[[i]]$family) {
      family <- confs[[entry]]$author[[i]]$family
      family %just% "Jr." <- ", Jr."
      given <- confs[[entry]]$author[[i]]$given
      the_person <- person(given = given, family = family)
    } else {the_person <- confs[[entry]]$author[[i]]}
    if (exists("auths")) {
      auths <- c(auths, the_person)
    } else {
      auths <- the_person
    }
  }
  confs[[entry]]$author <- auths
  rm(auths)
}
write_bib(confs, "conferences.bib")
print_refs("conferences.bib", c("long2019f",  "jeong2019", "long2019e"))
```

<!-- # Research in Progress -->

<!-- ```{r results = 'asis'} -->
<!-- print_refs("inprogress.bib", c("long", "longa", "jeonga", "jeong")) -->
<!-- ``` -->


# Under Review

```{r results = 'asis'}
print_refs("review.bib",  c("longa", "eveland", "long"))
```


# Teaching

## University of South Carolina

### Graduate 

* JOUR 717: Content Analysis
    * SP21

### Undergraduate

* JOUR 400: Digital Media and Big Data
    * AU20, SP21

## Ohio State University

### Undergraduate

* COMM 4820: Public Opinion and Communication
    * SU16

* COMM 3597: Media and Terrorism
    * AU18

* COMM 3554: Social Implications of Communication Technology
    * Online: SU18, SU19

* COMM 2367: Persuasive Communication
    * AU15, SP16, AU16 
    * Online: SP17, SU20
    
# Grants

SJMC Course Development Grant ($2000), University of South Carolina \hfill 2020

Omnibus Survey for the School of Communication, Ohio State University \hfill 2016



\phantom{.5in} with Michael Slater, Simon Lavis, and Min Seon Jeong

# Honors and Awards 

Chaffee-McLeod Top Student Paper Award, AEJMC CT\&M Division \hfill 2019 \thinspace \thinspace \thinspace

McCombs-Shaw Top Student Paper Award (2nd place), AEJMC PCIG \hfill 2019 \thinspace \thinspace \thinspace

University Fellowship (Ohio State University) \hfill 2014-15 

Mike Cody Award for Excellence in Political Science (Rhodes College) \hfill 2014 \thinspace \thinspace \thinspace

Sigma Tau Delta, International English Honor Society \hfill 2014 \thinspace \thinspace \thinspace

Pi Sigma Alpha, National Political Science Honor Society \hfill 2013 \thinspace \thinspace \thinspace

Cambridge Scholarship (Rhodes College) \hfill 2010-14 

Robert C. Byrd Honors Scholarship \hfill 2010-11 

# Professional Experience

## Copywriter, AndroidPolice.com \normalfont \hfill 2017-18
Wrote ad copy for clients who purchased native advertising on Android Police.

## Staff Writer, AndroidPolice.com \normalfont \hfill 2014-16
Android Police is a technology news website with over 5 million unique visitors per month. 

## Freelance, WMC-TV 5, \normalfont Memphis, TN \hfill 2011 \thinspace \thinspace \thinspace
Followed experience as news intern. Participated in editorial meetings, assisted reporters, anchors,
and producers, and worked assignment desk on weekends. Wrote content for newscasts and web.

<!-- \newpage -->

# Service

*Graduate Student Liaison*, AEJMC Comm. Theory & Methodology Division \hfill 2019-20

*Peer Mentor*, Ohio State University School of Communication \hfill 2019-20

## Journal Reviewing

* International Journal of Communication (2020)
* International Journal of Press/Politics (2020)
* Journal of Communication (2019)
* Media Psychology (2019, 2020)

## Conference Reviewing

*International Communication Association:*

* Mass Communication Division (2018)
* Political Communication Division (2018, 2019)
* Computational Methods Division (2019)

*Association for Education in Journalism and Mass Communication*:

* Political Communication Division (2019, 2020)

*National Communication Association:*

* Mass Communication Division (2017)
* Political Communication Division (2017)

<!-- # Additional Training -->

<!-- Social Network Analysis workshops at the *10th Annual Political Networks Conference*, Columbus, OH, May 2017 -->

<!-- Structural Equation Modeling Seminar by *Statistical Horizons*, Columbus, OH, August 2016  -->

<!-- \pagebreak -->

<!-- # References -->

<!-- \begin{multicols}{2} -->

<!-- \textbf{William P. ``Chip'' Eveland, Jr.} \\ -->
<!-- \textit{Professor of Communication} \\ -->
<!-- \textit{Professor of Political Science (by courtesy)} \\ -->
<!-- School of Communication \\ -->
<!-- The Ohio State University \\  -->
<!-- 3139 Derby Hall \\ -->
<!-- 154 North Oval Mall \\ -->
<!-- Columbus, OH 43210 \\ -->
<!-- \href{mailto:eveland.6@osu.edu}{eveland.6@osu.edu} -->

<!-- \textbf{Gerald M. Kosicki} \\ -->
<!-- \textit{Associate Professor} \\ -->
<!-- \textit{Section Head, Journalism Programs} \\ -->
<!-- School of Communication \\ -->
<!-- The Ohio State University \\  -->
<!-- 3138 Derby Hall \\ -->
<!-- 154 North Oval Mall \\ -->
<!-- Columbus, OH 43210 \\ -->
<!-- \href{mailto:kosicki.1@osu.edu}{kosicki.1@osu.edu} -->

<!-- \columnbreak -->

<!-- \textbf{Michael D. Slater} \\ -->
<!-- \textit{Social and Behavioral Sciences \\ Distinguished Professor \\ -->
<!-- Director}, School of Communication \\ -->
<!-- The Ohio State University \\  -->
<!-- 3022 Derby Hall \\ -->
<!-- 154 North Oval Mall \\ -->
<!-- Columbus, OH 43210 \\ -->
<!-- \href{mailto:slater.59@osu.edu}{slater.59@osu.edu} -->
<!-- \end{multicols} -->
