---
output: 
  pdf_document:
    latex_engine: xelatex
    template: "./cv-simple.tex"
    md_extensions: "-autolink_bare_uris -auto_identifiers"

name: "Jacob A. Long"

title: "Ph.D Candidate"
affiliation: "School of Communication \\hspace{.05in} \\textbullet \\hspace{.05in} Ohio State University"
contact:
  - text: "long.1377@osu.edu"
    link: "mailto:long.1377@osu.edu"
    icon: "EnvelopeO"
    mono: false
  - text: "jacob-long.com"
    link: "https://jacob-long.com"
    icon: "Globe"
    mono: true
  - text: "jacob-long"
    link: "https://github.com/jacob-long"
    icon: "Github"
    mono: true
  - text: "0000-0002-1582-6214"
    link: "https://orcid.org/0000-0002-1582-6214"
    acad: "Orcid"
    mono: true
# twitter: jacobandrewlong

bibs:
  - "pubbed.bib"
  - "conferences.bib"
  - "inprogress.bib"
  - "review.bib"

namehash: "7ee2eb84ac3fb6ae0cc177587fcaff6a"

raggedright: true

colorlinks: true
linkcolor: "blue"
urlcolor: "magenta"
---

```{r setup, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE, warn = FALSE, message = FALSE, comment = "")
```

# Education

## The Ohio State University \normalfont Columbus, Ohio, USA

* Ph.D Candidate, Communication \hfill expected 2020

    * Committee: 

        \smallskip

        William P. "Chip" Eveland, Jr. (advisor) 
        \hspace{.05in} \textbullet \hspace{.05in} Michael D. Slater
        \newline Gerald M. Kosicki
        \hspace{.05in} \textbullet \hspace{.05in} Robert M. Bond

        \smallskip

    * Graduate Interdisciplinary Specialization in Survey Research

* M.A., Communication \hfill 2019

## Rhodes College \normalfont Memphis, Tennessee, USA

* B.A. with Honors, Political Science \hfill 2014

    * Minors in Film Studies and English
    * Honors Thesis: "Understanding *The Daily Show with Jon Stewart*:
        Effects in a New Media Environment"
    * Advisors: Amy E. Jasperson and Rashna Wadia Richards

# Publications

```{r results = 'asis'}
library(RefManageR)
library(jtools)
print_refs <- function(file, names = NULL) {
  refs <- ReadBib(file, check = FALSE)
  cat(paste0("\\fullcitebib{", paste(
      c(names %just% names(refs), names(sort(refs, sorting = "ydnt")) %not% names), 
      collapse = ", "), "}"
    )
  )
}
print_refs("pubbed.bib")
```

# Under Review

```{r results = 'asis'}
print_refs("review.bib",  c("garrett"))
```


# Conference Presentations 

```{r results = 'asis'}
BibOptions(check.entries = FALSE)
confs <- ReadBib("conferences.bib")
for (entry in names(confs)) {
  if (is.null(confs[[entry]]$note)) {
    confs[[entry]]$note <- paste(
    ifelse(is.null(confs[[entry]]$type), no = confs[[entry]]$type, yes = "Paper"),
    "presented at the", confs[[entry]]$eventtitle
    )
    confs[[entry]]$type <- NULL
  }
}
WriteBib(confs, "conferences.bib")
print_refs("conferences.bib", c("long2019f", "long2019e"))
```

# Research in Progress

```{r results = 'asis'}
print_refs("inprogress.bib")
```

# Software

## R Packages

`jtools`: Analysis and presentation of social scientific data. 

```{r echo = FALSE}
library(rvest)
library(magrittr)
prof_url <- "https://scholar.google.com/citations?hl=en&user=fi-oVkIAAAAJ&view_op=list_works&citft=1&citft=2&email_for_op=jlongrc%40gmail.com&gmla=AJsN-F6U0W7Pb2H2sGdtSobMNTJR-HLu-OQ8kKCZeXg1EycF_GfWYLB54v7H5SlMcGBqKUjGlMnSkJlG3j0fM8wMhBJz2i4iM5kAVUf2PeoGyCMgeTkkLwA&gmla=AJsN-F7fklbe6gqvPjDweKtwwyvicMTZxtpVLPRUTNteYwXL1tMV7xHD81vwhCXcs_suOKGI83V7y8c_R5a_GxNBIkkarl0D6W7yKCwU2m9JqJ0Mzupk46M&sciund=729968478779288"
read_html(prof_url) %>%
  html_nodes("tr.gsc_a_tr") %>%
  .[stringr::str_detect(html_text(.), "jtools")] %>%
  html_children() %>%
  html_text() %>%
  .[2] -> jtools_gsch

library(jsonlite)
url <- paste0("https://cranlogs.r-pkg.org/downloads/total/2014-01-01:", Sys.Date(), "/jtools")
jtools_cranlogs <- fromJSON(url)[["downloads"]]
```

\small
\vspace{-.05in}

* \faiconn{r-project} [CRAN](https://CRAN.R-project.org/package=jtools) 
\hspace{.03in} \textbullet \hspace{.05in} 
\faGithub \hspace{.02in} [jacob-long/jtools](https://github.com/jacob-long/jtools)
\hspace{.03in} \textbullet \hspace{.05in} 
\faGlobe \hspace{.02in} [jtools.jacob-long.com](https://jtools.jacob-long.com)

* Author: **Jacob A. Long**
    * `r jtools_gsch` scholarly citations per
    [Google Scholar](https://scholar.google.com/scholar?oi=bibs&hl=en&cites=9332474636617245381,8245268343852705630) as of `r format(Sys.Date(), "%m/%d/%Y")`
    * `r format(jtools_cranlogs, big.mark = ",", scientific = FALSE)` downloads from RStudio's
    [CRAN mirror](https://r-pkg.org/services#cranlogs) as of `r format(Sys.Date(), "%m/%d/%Y")`

```{r echo = FALSE}
library(jsonlite)
url <- paste0("https://cranlogs.r-pkg.org/downloads/total/2014-01-01:", Sys.Date(), "/interactions")
interactions_cranlogs <- fromJSON(url)[["downloads"]]
```

\normalsize 

`interactions`: Comprehensive, user-friendly toolkit for probing interactions.

\small 
\vspace{-.05in}

* \faiconn{r-project} [CRAN](https://CRAN.R-project.org/package=interactions) 
\hspace{.03in} \textbullet \hspace{.05in} 
\faGithub \hspace{.02in} [jacob-long/interactions](https://github.com/jacob-long/interactions)
\hspace{.03in} \textbullet \hspace{.05in} 
\faGlobe \hspace{.02in} [interactions.jacob-long.com](https://interactions.jacob-long.com)
* Author: **Jacob A. Long**
    * `r format(interactions_cranlogs, big.mark = ",", scientific = FALSE)` downloads from RStudio's
    [CRAN mirror](https://r-pkg.org/services#cranlogs) as of `r format(Sys.Date(), "%m/%d/%Y")`
    * Highlighted as a [top new package](https://rviews.rstudio.com/2019/03/26/february-2019-top-40-new-cran-packages/)
     in February 2019

\normalsize

`panelr`: Regression models and utilities for repeated measures and panel data.

```{r echo = FALSE}
library(jsonlite)
url <- paste0("https://cranlogs.r-pkg.org/downloads/total/2014-01-01:", Sys.Date(), "/panelr")
panelr_cranlogs <- fromJSON(url)[["downloads"]]
```

\small 
\vspace{-.05in}

* \faiconn{r-project} [CRAN](https://CRAN.R-project.org/package=panelr) 
\hspace{.03in} \textbullet \hspace{.05in} 
\faGithub \hspace{.02in} [jacob-long/panelr](https://github.com/jacob-long/panelr)
\hspace{.03in} \textbullet \hspace{.05in} 
\faGlobe \hspace{.02in} [panelr.jacob-long.com](https://panelr.jacob-long.com)
* Author: **Jacob A. Long**
    * `r format(panelr_cranlogs, big.mark = ",", scientific = FALSE)` downloads from RStudio's
    [CRAN mirror](https://r-pkg.org/services#cranlogs) as of `r format(Sys.Date(), "%m/%d/%Y")`

\normalsize

`dpm`: Dynamic panel models fit with maximum likelihood. 
\small 
\vspace{-.05in}

* \faGithub \hspace{.02in} [github.com/jacob-long/dpm](https://github.com/jacob-long/dpm)
\hspace{.03in} \textbullet \hspace{.05in} 
\faGlobe \hspace{.02in} [dpm.jacob-long.com](https://dpm.jacob-long.com)

* Authors: **Jacob A. Long**, Richard A. Williams, Paul D. Allison

\normalsize

## Other

Song and Lyric Data Scraper [Ruby app]. Accompanies Long \& Eveland (2019). 

\vspace{-.05in}

* doi:[10.5281/zenodo.1203368](https://doi.org/10.5281/zenodo.1203368)

\small 
\vspace{-.07in}

* \faGithub \hspace{.02in} [github.com/jacob-long/song-and-lyric-data-scraper](https://github.com/jacob-long/song-and-lyric-data-scraper) 

\normalsize

\newpage 

# Teaching

## Ohio State University

* COMM 4820: Public Opinion and Communication
    * Summer 2016

* COMM 3597: Media and Terrorism
    * Autumn 2018

* COMM 3554: Social Implications of Communication Technology
    * Summer 2018, 2019 (taught online)

* COMM 2367: Persuasive Communication
    * Autumn 2015, Spring 2016 (2 sections), Autumn 2016 (2 sections), Spring 2017 (taught online)

# Honors and Awards

Chaffee-McLeod Top Student Paper Award, AEJMC CT\&M Division \hfill 2019 \thinspace \thinspace \thinspace

University Fellowship (Ohio State University) \hfill 2014-15 

Mike Cody Award for Excellence in Political Science (Rhodes College) \hfill 2014 \thinspace \thinspace \thinspace

Sigma Tau Delta, International English Honor Society \hfill 2014 \thinspace \thinspace \thinspace

Pi Sigma Alpha, National Political Science Honor Society \hfill 2013 \thinspace \thinspace \thinspace

Cambridge Scholarship (Rhodes College) \hfill 2010-14 

Robert C. Byrd Honors Scholarship \hfill 2010-11

# Professional Experience

## Freelance, WMC-TV 5, \normalfont Memphis, TN
Followed experience as news intern. Participated in editorial meetings, assisted reporters, anchors,
and producers, and worked assignment desk on weekends. Wrote content for newscasts and web.

# Service

## Conference Reviewing

*International Communication Association:*

* Mass Communication Division (2018)
* Political Communication Division (2018, 2019)
* Computational Methods Interest Group (2019)

*Association for Education in Journalism and Mass Communication*:

* Political Communication Interest Group (2019)

*National Communication Association:*

* Mass Communication Division (2017)
* Political Communication Division (2017)

<!--# Additional Training

Social Network Analysis workshops at the *10th Annual Political Networks Conference*, Columbus, OH, May 2017

Structural Equation Modeling Seminar by *Statistical Horizons*, Columbus, OH, August 2016 -->
