
% Based on template shared by Chris Paciorek at http://www.stat.berkeley.edu/~paciorek/computingTips/Latex_template_creating_CV_.html

\documentclass[margin,line]{res}

\usepackage[colorlinks=true, urlcolor=blue]{hyperref}


\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
% if using pdflatex:
%\setlength{\pdfpagewidth}{\paperwidth}
%\setlength{\pdfpageheight}{\paperheight} 

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\begin{document}

\name{Jacob A. Long \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{2in}p{4in}}
Derby Hall 3001           & {\it Voice:}  (815) 822-2991 \\            
School of Communication & {\it E-mail:}  \href{mailto:long.1377@osu.edu}{\nolinkurl{long.1377@osu.edu}}\\         
Ohio State University & {\it Web:} \url{www.jacob-long.com}\\ 
154 N. Oval Mall \\      
Columbus, OH, 43214 USA \\     
\end{tabular}


\section{\sc Research Interests}
Political communication, mass communication, deliberation, moral psychology, political entertainment, communication technology

\section{\sc Education}
{\bf The Ohio State University}, Columbus, Ohio USA\\
%{\em School of Communication} 
\vspace*{-.1in}
\begin{list1}
\item[] Ph.D. Student, Communication, (expected graduation: 2019)
\begin{list2}
\vspace*{.05in}
%\item Dissertation Topic:  ``Nonstationary Covariance Models for Spatial Data and Regression Problems'' 
\item Advisor: Dr. William P. "Chip" Eveland
\end{list2}
%\vspace*{.05in}
%\item[] M.A., Communication, 2016
\end{list1}

{\bf Rhodes College}, Memphis, Tennessee USA\\
\vspace*{-.1in}
\begin{list1}
\item[] B.A. with Honors, Political Science,  May, 2014
\begin{list2}
\vspace*{.05in}
\item  Minors in Film Studies and English
\item Thesis Title: ``Understanding {\em The Daily Show with Jon Stewart}: Effects in a New Media Environment''
\item Advisor: Dr. Amy E. Jasperson
\end{list2}
\end{list1}

% \section{\sc Academic Experience}
% {\bf Carnegie Mellon University}, Pittsburgh, Pennsylvania USA

% \vspace{-.3cm}
% {\em Graduate Student} \hfill {\bf August, 1998 - present}\\
% Includes current Ph.D.~research, Ph.D.~and Masters level coursework and
% research/consulting projects.

% %\vspace{-.1cm}
% {\em Instructor} \hfill {\bf May - June, 2002}\\
% Co-taught graduate level course for the Master of Science in
% Computational Finance program.  Shared responsibility for lectures, exams,
% homework assignments, and  grades.  
% \vspace*{.05in}  
% \begin{list2}
% \item 46-731 Probability and Statistics, Summer 2002.
% \end{list2}


% %\vspace{-.1cm}
% {\em NSF VIGRE Teaching Fellow} \hfill {\bf January - May, 2001}\\
% Head teaching assistant.   
% Duties included  shared administrative responsibilities with faculty
% instructor, fielding of all student inquiries, and oversight of
% graduate student teaching assistants and graders.
% \vspace*{.05in}  
% \begin{list2}
% \item 36-217 Probability Theory and Random Processes, Spring 2001.
% \end{list2}

% %\vspace{-.1cm}
% {\em Teaching Assistant} \hfill {\bf August, 2001  - present}\\
% Duties at various times have included 
% office hours and leading weekly computer lab exercises.



% \section{\sc Publications}
% Paciorek, C.J., J.S. Risbey, V. Ventura, and R.D.Rosen. 2002. Multiple indices of Northern Hemisphere Cyclone
% Activity, Winters 1949-1999. Journal of Climate 15:1573-1590.

% Paciorek, C.J., R. Condit, S.P. Hubbell, and R.B. Foster.  2000.
% The demographics of resprouting in tree and shrub species of a moist
% tropical forest.  Journal of Ecology 88:765-777.

% Paciorek, C.J., B.R. Moyer, R.A. Levin, and S.L. Halpern.  1995.
% Pollen consumption by hummingbird flower mite {\it Proctolaelaps
%   kirmsei} and possible fitness effects on {\it Hamelia patens}.
% Biotropica 27:258-262.  (author order determined by lot)     

% \section{\sc Papers in preparation}

% Ventura, V., C.J. Paciorek, and J.S. Risbey.  Controlling the proportion of falsely-rejected hypotheses when conducting multiple tests with geophysical data.

% Ickes, K., C.J. Paciorek, and S. Thomas.  Effects of wild pigs on
% forest demographic processes in Malaysia.

% \section{\sc Conference Presentations}
% Paciorek, C.J., J.S. Risbey, V. Ventura, and R.D.Rosen.  2001.  Changes in Northern Hemisphere winter storm activity (1949-1999) based
% on a comparison of cyclone indices.  8th International Meeting on
% Statistical Climatology, Luneberg, Germany, March, 2001.

% Paciorek, C.J. and R. Rosenfeld.  2000.  Minimum classification error
% training in exponential language models.  2000 Spring Transcription
% Workshop, College Park, Maryland.
% \vspace*{-.25in}  
% \begin{verbatim}http://www.nist.gov/speech/publications/tw00/html/abstract.htm#cp1-50\end{verbatim}

\section{\sc Conference Presentations}

{\bf Long, J.A.}, Eveland, W.P., Jr., \& Slater, M.D. (2017, May). \emph{Partisan media selectivity and partisan identity threat: The role of social and geographic context}. Paper presented to the Annual Conference of the International Communication Association, San Diego, CA.

Jeong, M. \&  {\bf Long, J.A.} (2016, November). \emph{Sharing and discussing politics on Facebook: A user and network-centric approach}. Paper presented to the National Communication Assocation Annual Convention, Philadelphia, PA.

{\bf Long, J.A.} \& Eveland, W. P., Jr. (2015, November). \emph{The political and moral relevance of popular music: Matching worldviews with lyrical content}. Paper presented to the Midwest Association for Public Opinion Research, Chicago, IL.

%{\bf Long, J.A.} (2014, April). \emph{Getting film (studies) in on the act: Mediated citizenship and the movies}. Paper presented to the annual Rhodes-Hendrix Film Studies Symposium, Memphis, TN.

{\bf Long, J.A.} (2014, February). \emph{The death of 'soft news'}. Paper presented to the annual meeting of the Southwest Popular/American Culture Association, Albuquerque, NM.

%{\bf Long, J.A.} (2013, April). \emph{Masculinity and transational Spanish stardom in} Celda 211. Paper presented to the annual Symposium on Gender and Sexuality Studies, Memphis, TN.

\section{\sc Honors and Awards} 
University Fellowship (Ohio State University), 2014-15.

\vspace*{-2.5mm}
Mike Cody Award for Excellence in Political Science (Rhodes College), 2014.

\vspace*{-2.5mm}
Pi Sigma Alpha, National Political Science Honor Society, 2013.

\vspace*{-2.5mm}
Cambridge Scholarship (Rhodes College), 2010-14.

\section{\sc Research In Progress} 

{\sc Under Review}\\
\textbf{Long, J.A.} \& Eveland, W.P., Jr. \emph{Entertainment use and political ideology: Linking worldviews to media content}. Manuscript under review.

\textbf{Long, J.A.} \emph{Can a balanced political media diet depolarize a partisan public? The competing effects of partisan and nonpartisan sources}. Manuscript under review.

Kleinman, S.B., Eveland, W.P., Jr., \& \textbf{Long, J.A.} \emph{Inferring preferences without talking: Using limited visual information to guide political discussant choice via homophily}. Conference submission under review.

{\sc In Preparation}\\
Slater, M.D., Jeong, M., Lavis, S.M., \& {\bf Long, J.A.} \emph{Political news and entertainment content: Motivation, selection, and experience in a presidential election cycle}. Omnibus Survey for the Ohio State School of Communication Data collection completed January 2017. 

%{\sc Data Collection}\\


\section{\sc Teaching Experience}
{\bf Ohio State University}

\vspace*{-2.5mm}
\emph{Spring 2017}: COMM 2367: Persuasive Communication. Taught online. (2 sections)

\vspace*{-2.5mm}
\emph{Fall 2016}: COMM 2367: Persuasive Communication. (2 sections)

\vspace*{-2.5mm}
\emph{Summer 2016}: COMM 4820: Public Opinion and Communication.

\vspace*{-2.5mm}
\emph{Spring 2016}: COMM 2367: Persuasive Communication. (2 sections)

\vspace*{-2.5mm}
\emph{Autumn 2015}: COMM 2367: Persuasive Communication.

\section{\sc Professional Experience}
{\bf Freelance}, WMC-TV 5, Memphis, TN\\
Followed experience as news intern. Participated in editorial meetings, assisted reporters, anchors, and producers, and worked assignment desk on weekends. Wrote content for newscasts and web.

% \vspace{-.3cm}

% \vspace{-.3cm}

\section{\sc Software} 

\textbf{jtools}: Analysis and Presentation of Social Scientific Data [R Package]. \url{https://CRAN.R-project.org/package=jtools}

\section{\sc Computer Skills} 
\begin{list2}
\item Statistical Packages:  R, SPSS, Stata.
\item Applications: \LaTeX
\item Programming Languages: Ruby, Python\\ 
\end{list2}



\end{resume}
\end{document}




